### 2021-07-20 README.Rmd
link to documentation in readme

The "Basic Usage" vignette steps through the primary functionality of the `skater` package:

@@

>>>>

The ["Basic Usage" vignette](https://signaturescience.github.io/skater/articles/basic_usage.html) steps through the primary functionality of the `skater` package:

@@

Full documentation: <https://signaturescience.github.io/skater/>.
